Insert the article title here

### 2020-07-24 tex/results.tex
fix mising sentence
resize figure to stop warning
made a comment on extra peaks

We decided to replicate one of the results that they present on Fig.14 of their paper, which 
presents the scattering cross section of a SiC rectangular cylinder for three different object 
sizes. To comply with our quasistatic approach ($\lambda > d$ where $d$) we chose the particular 
case where a=672 nm and b=328 nm.

@@

\begin{figure}
    \centering
    \includegraphics[width=0.85\textwidth]{AR_22_vs_norm.pdf} 
    \caption{Extinction cross section across wave number for SiC pillars of multiple aspect ratios,  
             (H=950 nm, W=400nm, L=400-2800 nm (AR=1-7)), where we have normal incidence and a 
             22 degrees incidence.
            }
    \label{fig:AR_22_vs_norm}
 \end{figure}

@@

Since our simulations do not count for coupling effects, we can not strictly imitate 
the conditions to validate our solver. However, from Figure S4 on the supplementary 
material of Ellis et al, we know that coupling effects affect the $E^{\parallel}_{100}$ 
mode by a shift of 12.17 cm$^-1$. Therefore as a \textit{first order correction} we can 
subtract this value from our simulations, to contemplate for coupling effects. In Figure 
\ref{fig:val_2a} we present the result after applying the correction for coupling effects.

>>>>

We decided to replicate one of the results that they present on Fig.14 of their paper, which 
presents the scattering cross section of a SiC rectangular cylinder for three different object 
sizes. To comply with our quasistatic approach ($\lambda > d$ where $d$ is the characteristic
dimension of the geometry) we chose the particular case where a=672 nm and b=328 nm.

@@

\begin{figure}
    \centering
    \includegraphics[width=0.8\textwidth]{AR_22_vs_norm.pdf} 
    \caption{Extinction cross section across wave number for SiC pillars of multiple aspect ratios,  
             (H=950 nm, W=400nm, L=400-2800 nm (AR=1-7)), where we have normal incidence and a 
             22 degrees incidence.
            }
    \label{fig:AR_22_vs_norm}
 \end{figure}

@@

Since our simulations do not count for coupling effects, we can not strictly imitate 
the conditions to validate our solver. However, from Figure S4 on the supplementary 
material of Ellis et al, we know that coupling effects affect the $E^{\parallel}_{100}$ 
mode by a shift of 12.17 cm$^-1$. Therefore as a \textit{first order correction} we can 
subtract this value from our simulations, to contemplate for coupling effects. In Figure 
\ref{fig:val_2a} we present the result after applying the correction for coupling effects.
It is worth mentioning that the far left (837 cm$^-1$) and far right (964 cm$^-1$) peaks 
on Ellis results, are peaks associated with zone-folded LO (longitudinal) phonons, in 
particular P1 (837 cm$^-1$) is not infrared active \cite{ellis2016}. Ellis and coworkers, 
do not discuss this result into detail, but they concentrate their analysis on the peaks
that happen between 864–961 cm$^-1$
